\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2015-12-09 paper/Paper_sweave.Rnw
fix author order

\if0\blind
{
\author{Dianne Cook\\
Department of Econometrics and Business Statistics, Monash University\\
and\\
Nathaniel Tomasetti\\
Department of Econometrics and Business Statistics, Monash University\\}
  \maketitle
} \fi
\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Comparing the Power of Plot Designs to Reveal Correlation}
\end{center}
  \medskip
} \fi

>>>>

\if0\blind
{
\author{Nathaniel Tomasetti and Dianne Cook\\
Department of Econometrics and Business Statistics, Monash University\\
}
  \maketitle
} \fi
\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Comparing the Power of Plot Designs to Reveal Correlation}
\end{center}
  \medskip
} \fi
